Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-01 WSSSPE2_report/WSSSPE2_review.tex
Update due date. Section 4:  Add a few notes from Dan.

\author{TBD by contributions \\{\scriptsize\today \quad  (Due:  $\backsim$ April 1)}} 
%\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$, Nancy Wilkins-Diehr$^{(8)}$,
%Richard Littauer$^{(9)}$,
%Miguel de Val-Borro$^{(10)}$, 
%Sou-Cheng T. Choi$^{(11)}$}
%
%\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA}
%
%\thanks{{}$^{(2)}$ University of Illinois, Champaign, IL, USA}
%
%\thanks{{}$^{(3)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
%\thanks{{}$^{(8)}$ University of California-San Diego, San Diego, CA, USA}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}
%
%\thanks{{}$^{(11)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}

\choinote{To extend deadline to after April 1?}

@@

@@

The WSSSPE2 workshop continues our experiment from WSSSPE1 in how we can
collaboratively build a workshop agenda. The differences in WSSSPE2 from WSSSPE1
are in using an existing service (EasyChair) to handle submissions and reviews,
rather than an ad hoc process, and using an existing service (well-sorted) to
allow collaborative grouping of papers into themes by all authors, reviewers,
and the community, rather than this being done in an ad hoc manner by the
organizers alone. \choinote{Are lightning talks a new feature in WSSSPE2?}
\katznote{yes, along with a change to breakout groups that were intended to
define actions, then potentially become longer lasting working groups to perform
those actions} \choinote{Since lightning talks is confirmed a new feature in
WSSSPE2, shall it be recorded somewhere in an earlier section?} \katznote{yes, please feel free to add something in the abstract and intro - maybe we also need a new section after keynotes for lightning talks?}

>>>>

\author{TBD by contributions \\{\scriptsize\today \quad  (Due:  $\backsim$ April 30)}} 
%\author{Daniel S. Katz$^{(1)}$, Gabrielle Allen$^{(2)}$, Neil Chue Hong$^{(3)}$, \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$, Nancy Wilkins-Diehr$^{(8)}$,
%Richard Littauer$^{(9)}$,
%Miguel de Val-Borro$^{(10)}$, 
%Sou-Cheng T. Choi$^{(11)}$}
%
%\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA}
%
%\thanks{{}$^{(2)}$ University of Illinois, Champaign, IL, USA}
%
%\thanks{{}$^{(3)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
%\thanks{{}$^{(8)}$ University of California-San Diego, San Diego, CA, USA}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}
%
%\thanks{{}$^{(11)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}

@@

\note{Lead: Choi. Volunteers welcome.
\href{http://wssspe.researchcomputing.org.uk/wssspe2/lightning-talks/}{Slides}}

Lightning talks is a new feature in WSSSPE2. Every talk in it were given only 2
minutes.

\katznote{You could write to everyone and ask for a short summary of their talks
- perhaps 1-3 sentences}

\katznote{yes, along with a change to breakout groups that were intended to
define actions, then potentially become longer lasting working groups to perform
those actions}

\katznote{yes, please feel free to add something in the abstract and intro}

@@

The WSSSPE2 workshop continues our experiment from WSSSPE1 in how we can
collaboratively build a workshop agenda. The differences in WSSSPE2 from WSSSPE1
are in using an existing service (EasyChair) to handle submissions and reviews,
rather than an ad hoc process, and using an existing service (well-sorted) to
allow collaborative grouping of papers into themes by all authors, reviewers,
and the community, rather than this being done in an ad hoc manner by the
organizers alone.
